Universal Anonymous Signatures

### 2022-10-04 prism-backend/research/gsac/preliminaries-paper.tex
30 pages.

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, and commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
\SBCMBlind,\SBCMSign,\SBCMUnblind,\SBCMVerify).
%
Algorithm $\parm \gets \SBCMSetup(\secpar)$ produces the public parameters for
the scheme.
% 
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing key pair.
%
$(\Ccom,\pi,r) \gets \SBCMBlind^{\NIZKRel}(\vk,\osmsg,\smsg;x',w')$ is run by a
user who wants to request a signature over $\osmsg \cup \smsg$, where only \smsg
are revealed to the signer, and $\osmsg$ are to be signed in committed form.
Moreover, \osmsg (and, possibly, $w'$) are witnesses to some statement defined
over \smsg (and, possibly, $x'$), for a relationship \NIZKRel.
%
$\bsig \gets \SBCMSign^{\NIZKRel}(\sk,\Ccom,\pi,\smsg; x')$ is run by the
signer, to produce a partial signature \bsig over a set of committed
messages and set \smsg, satisfying relation \NIZKRel.
%
$\sig \gets \SBCMUnblind^{\NIZKRel}(\vk,\bsig,\Ccom,r,\osmsg,\smsg)$ is
run by the user to complete a partial signature \bsig received by the
signer, over \osmsg (committed to in \Ccom) and \smsg.
%
Finally, algorithm $1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$ verifies a
signature \sig over message vector $\osmsg \cup \smsg$.
%
In addition, the produced signatures must be compatible with (efficient) NIZK
proofs of knowledge of a signature, and of (arbitrary) claims over the signed
(committed) messages. An \SBCM scheme must provide one-more-forgery type of
security.

>>>>

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, and commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
We define such schemes as a tuple (\SBCMSetup, \SBCMKeyGen,
\SBCMBlind, \SBCMSign, \SBCMUnblind, \SBCMVerify).
%
Algorithm $\parm \gets \SBCMSetup(\secpar)$ produces the public parameters for
the scheme.
% 
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing key pair.
%
$(\Ccom,\pi,r) \gets \SBCMBlind^{\NIZKRel}(\vk,\osmsg,\smsg;x',w')$ is run by a
user to request a signature over $\osmsg \cup \smsg$, where \smsg are revealed
to the signer, but \osmsg are signed in committed form.
Moreover, \osmsg (and, possibly, $w'$) are witnesses to some statement defined
over \smsg (and, possibly, $x'$), for a relationship \NIZKRel.
%
$\bsig \gets \SBCMSign^{\NIZKRel}(\sk,\Ccom,\pi,\smsg; x')$ is run by the
signer, to produce a partial signature \bsig over a set of committed
messages \osmsg and set \smsg, satisfying relation \NIZKRel.
%
$\sig \gets \SBCMUnblind^{\NIZKRel}(\vk,\bsig,\Ccom,r,\osmsg,\smsg)$ is
run by the user to complete a partial signature \bsig received by the
signer.
%
Finally, algorithm $1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$ verifies a
signature \sig over message vector $\osmsg \cup \smsg$.
%
In addition, the produced signatures must be compatible with (efficient) NIZK
proofs of knowledge of a signature, and of (arbitrary) claims over the signed
(committed) messages. An \SBCM scheme must provide one-more-forgery type of
security.

### 2022-10-04 prism-backend/research/gsac/relationships.tex
30 pages.

In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
models of related schemes in the literature.
Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
that they securely instantiate the models for the presented schemes, if the
corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
we rely on the functions described in \figref{fig:func-restrictions}. Observe
that all the \fissue functions listed in \figref{fig:func-restrictions} are
\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
\UAS-acceptable if $H$ is a secure PRF \cite{kl14}.

@@

We adopt the model in \cite{bsz05}. In this abstraction of group signatures, the
opener returns an index uniquely identifying the group member that created a
signature, along with a correctness proof. For ease of exposition, assume that,
without loss of generality, this index is just the public key that the group
member generates randomly when joining the group\footnote{The user public key is
  assumed to be
  accessible from a public table in \cite{bsz05}, so it is easy to translate the
  public key into an index, if needed.}. A group signature scheme, according to
\cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
\Judge algorithms, as well as an $\langle\Obtain,\Issue\rangle$ interactive
protocol. Their intuition is similar to that of \UAS, so we refer to
\cite{bsz05} for detailed descriptions. For ease of reference, we replicate the
security games in \figref{fig:model-gs}.

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $H$ is a
PRF. In that case, its output is a random-looking string that depends on the
user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
will be the same per $(I,\upk)$ pair, and can be used by issuer $I$ to prevent
issuing more than one credential per user. Basically, the issuer maintains a
list of received $\yissue = H(I,\upk)$ values, and rejects issuing a credential
for already existing ones. From this, the GS algorithms are as
follows:

@@

\paragraph{Security of \CUASGS.} %
Our \CUASGS construction is an anonymous, traceable, and non-frameable group
signature scheme, according to the model in \cite{bsz05}. For space constraints,
proofs are deferred to \appref{app:related-proofs}.

@@

\subsubsection{\CUASRing Construction.} %
We can use a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of \CUASGenHideIss to build a ring signature scheme according to the model
in \figref{fig:model-rs}. In a nutshell, we let users self-issue
credentials where the attributes are (a subset of encodings of) the public keys
of the users in the system -- including their own public key. Then, a ring
signature is just a \CUASGenHideIss signature that reveals a subset of
the attributes -- i.e., a subset of the keys of the users in the system. In more
detail, the construction is as follows:

@@

\paragraph{Security of \CUASRing.} %
Our \CUASRing construction is an anonymous and unforgeable ring signature
scheme, according to the model in \cite{bkm06}. For space constraints,
proofs are deferred to \appref{app:related-proofs}.

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure, which restricts to one credential per presentation. Therein, an
anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
$IssKeyGen$), and $UserKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols. We
refer to \cite{fhs19} for the full details. For ease of reference, we give
the security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

\subsubsection{\CUASAC Construction.} %
We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGenInt
restriction, is a secure anonymous credential scheme according to the model in
\cite{fhs19}. We first quickly define the algorithms, and then prove security.

@@

\paragraph{Security of \CUASAC.} %
Our \CUASAC construction is an anonymous and unforgeable anonymous credential
scheme, according to the model in \cite{fhs19}. For space constraints,
proofs are deferred to \appref{app:related-proofs}.

>>>>

In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
models of related schemes in the literature.
Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
that they securely instantiate the models for the presented schemes, if the
corresponding \CUASGen restriction is a secure \UAS construction. For lack of
space, security proofs are deferred to \appref{app:related-proofs}.

For the described \CUASGen restrictions, we rely on the functions described in
\figref{fig:func-restrictions}. Observe that all the \fissue functions listed in
\figref{fig:func-restrictions} are \UAS-acceptable. Specifically, $\fissue^1$
and $\fissue^{\sring}$ are trivially \UAS-acceptable (for $\rngfissue = \bin$);
whereas $\fissue^{single,H,I}$ is \UAS-acceptable if $H$ is a secure PRF
\cite{kl14}.

@@

We adopt the model in \cite{bsz05}. In this abstraction, the opener returns an
index uniquely identifying the group member who created a signature, along with
a correctness proof. To ease exposition, we assume without loss of generality
that this index is just the public key that group members generate randomly
when joining the group\footnote{The user public key is
  assumed to be
  accessible from a public table in \cite{bsz05}, so it is easy to translate the
  public key into an index, if needed.}. A group signature scheme in
\cite{bsz05} is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
\Judge algorithms, and an $\langle\Obtain,\Issue\rangle$ interactive
protocol. Their intuition is similar to that of \UAS, so we refer to
\cite{bsz05} for detailed descriptions. For ease of reference, we replicate the
security games in \figref{fig:model-gs}.

@@

\subsubsection{\CUASGS construction.} %
We show that a $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction is a secure group signature scheme according to \cite{bsz05}.
As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $H$ is a
PRF, as its output is a random-looking string that depends on the user public
key \upk, and a string $I$ uniquely identifying the issuer. Thus, it is the same
per $(I,\upk)$ pair, and can be used by issuer $I$ to prevent issuing more than
one credential per user. Basically, the issuer keeps a list of received
$\yissue = H(I,\upk)$ values, and rejects issuing a credential for already
existing ones. From this, the GS algorithms are as follows:

@@

% \paragraph{Security of \CUASGS.} %
% Our \CUASGS construction is an anonymous, traceable, and non-frameable group
% signature scheme, according to the model in \cite{bsz05}. For space constraints,
% proofs are deferred to \appref{app:related-proofs}.

@@

\subsubsection{\CUASRing Construction.} %
We use a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of \CUASGenHideIss to build a ring signature scheme in the model given in
\figref{fig:model-rs}. Briefly, users self-issue credentials where the
attributes are (encodings of) the public keys of the users in the system --
including their own public key. Then, a ring signature is just a
\CUASGenHideIss signature that reveals a subset of the attributes -- i.e., a
subset of the keys of the users in the system. The construction
is as follows:

@@

% \paragraph{Security of \CUASRing.} %
% Our \CUASRing construction is an anonymous and unforgeable ring signature
% scheme, according to the model in \cite{bkm06}. For space constraints,
% proofs are deferred to \appref{app:related-proofs}.

@@

We adopt the model in \cite{fhs19} for anonymous credentials with selective
disclosure, which restricts to one credential per presentation. Therein, an
anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
$IssKeyGen$), and $UserKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols. We
refer to \cite{fhs19} for the full details. For readability, we give
the security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

\subsubsection{\CUASAC Construction.} %
We build a secure anonymous credential scheme directly from a
$(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGenInt restriction.

@@

% \paragraph{Security of \CUASAC.} %
% Our \CUASAC construction is an anonymous and unforgeable anonymous credential
% scheme, according to the model in \cite{fhs19}. For space constraints,
% proofs are deferred to \appref{app:related-proofs}.
